Best Practices for Single Alchemical Free Energy Calculations [Article v\versionnumber]

### 2025-12-09 paper/manuscript.tex
Fix citation key error

To derive an RBFE formulation from double-decoupling, we write expressions for the binding constants of $A$ and $B$ using Eq.~(\ref{eq:ddm-ratios-1}) and taking their ratio. While doing so, the standard state, pure solvent, and gas-phase terms cancel, and we obtain
\begin{equation}\label{eq:double-transformation-Kb-rbfe}
\frac{K_b(B)}{K_b(A)} = \frac{Z_{N_v,RB}}{Z_{N_v,RA}} \frac{Z_{N_v,A}}{Z_{N_v,B}}
\end{equation}
where the first ratio of partition functions involves receptor-ligand complexes and the second only the ligands in solution. Eq.~(\ref{eq:double-transformation-Kb-rbfe}), suggests that the relative binding free energy, $\Delta \Delta G_b$, of $B$ relative to $A$ can be expressed as the difference of the free energies, $\Delta G_{\rm bound}$ and $\Delta G_{\rm unbound}$, of ``mutating'' ligand $A$ into ligand $B$ in the presence and absence of the receptor, respectively (Figure \ref{fig:fig_binding_thermodynamic_cycle}):~\cite{tembre1984ligandreceptor,gilson1997statisticalthermodynamic,mobley2012perspective,cournia2017relative,jiang2019computing,lee_jcheminfmodel_2020_v60_p5595}
\begin{equation}\label{eq:double-transformation-dg-rbfe}
\Delta \Delta G_b = -k_B T \ln \frac{Z_{N_v,RB}}{Z_{N_v,RA}} - (-k_B T \ln \frac{Z_{N_v,B}}{Z_{N_v,A}}) = \Delta G_{\rm bound} - \Delta G_{\rm unbound}
\end{equation}

>>>>

To derive an RBFE formulation from double-decoupling, we write expressions for the binding constants of $A$ and $B$ using Eq.~(\ref{eq:ddm-ratios-1}) and taking their ratio. While doing so, the standard state, pure solvent, and gas-phase terms cancel, and we obtain
\begin{equation}\label{eq:double-transformation-Kb-rbfe}
\frac{K_b(B)}{K_b(A)} = \frac{Z_{N_v,RB}}{Z_{N_v,RA}} \frac{Z_{N_v,A}}{Z_{N_v,B}}
\end{equation}
where the first ratio of partition functions involves receptor-ligand complexes and the second only the ligands in solution. Eq.~(\ref{eq:double-transformation-Kb-rbfe}), suggests that the relative binding free energy, $\Delta \Delta G_b$, of $B$ relative to $A$ can be expressed as the difference of the free energies, $\Delta G_{\rm bound}$ and $\Delta G_{\rm unbound}$, of ``mutating'' ligand $A$ into ligand $B$ in the presence and absence of the receptor, respectively (Figure \ref{fig:fig_binding_thermodynamic_cycle}):~\cite{tembre1984ligandreceptor,gilson1997statisticalthermodynamic,mobley2012perspective,cournia2017relative,jiang2019computing, Lee_JChemTheoryComput_2020_v16_p5512}
\begin{equation}\label{eq:double-transformation-dg-rbfe}
\Delta \Delta G_b = -k_B T \ln \frac{Z_{N_v,RB}}{Z_{N_v,RA}} - (-k_B T \ln \frac{Z_{N_v,B}}{Z_{N_v,A}}) = \Delta G_{\rm bound} - \Delta G_{\rm unbound}
\end{equation}
